---
title: "Tutorial 7"
author: "Ananya_Gupta"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(survey)
library(Hmisc)
library(ggplot2)
library(readxl)
library(GGally)
library(gridExtra)
```

**Display of the revised data tibble**
```{r data, echo=FALSE}
respondents<-read_excel("../data/happ_svy_data.xlsx")
#describe(respondents)

colnames(respondents)<-c("Q1","Q2","Q3","Q4","Q5","Q6","Q7","Q8","Q9","Q10","Q11","Q12","Q13","Q14","Q15","Q16","Q17","Q18","Q19","Q20","Q21","Q22","Q23","Q24","Q25","Q26","Q27","Q28","Q29", "Citizenship","Location","Gender")

changed<-respondents %>%
  select(1:29) %>%
  lapply(function(x) recode(x,"Strongly disagree"=1,"Moderately disagree"=2,"Slightly disagree"=3,"Slightly agree"=4,"Moderately agree"=5,"Strongly agree"=6)) %>%
  as_tibble()
  
#reverse
reversed<-changed %>%
  select(1,5,6,10,13,14,19,23,24,25,27,28,29) %>% 
  lapply(function(y) 7-y) %>%
  as_tibble()

final<-cbind(respondents[,c(30,31,32)],
             changed[,c(2:4,7:9,11,12,15:18,20:22,26)],
             reversed)

#adding threshold population (fpc) and id no.s
df<-rep(105,times=73)
id<-seq(1,73,by=1)

final<-final %>%
  mutate(add=rowSums(across(c(4:32)))) %>%
  mutate(happ_score=add/29) %>%
  select(1:3,34) %>%
  mutate(id,df)%>%
  relocate(id,.before=1)

final[c(1,2),]

```

**Raking of the data**
```{r raking, echo=FALSE}

des<-svydesign(id=~id,data=final, fpc=~df)
pop.gender <- data.frame(Gender=c("M", "F"), Freq=c(65, 40))

#before raking mean,error
#svymean(~happ_score, design=des)

#after raking mean,error
des.raked <- rake(des,sample=list(~Gender),population=list(pop.gender)) 
svymean(~happ_score, design=des.raked)

```

**Plot 1: Visualising happiness level of male and female from each combination category**

- International, off-campus males have the lowest happiness level
- Singaporean/PR, on-campus females have the highest happiness level
- Singaporean/PR students overall seem to be more happier than foreigners (maybe due to homesickness and more responsibilities for foreigners)
- Location seems to be a less affecting variable as it has varying results for each combination

```{r plot1, echo=FALSE, fig.height=3}
final %>%
  ggplot()+
  geom_col(aes(x=Gender,y=happ_score,fill=Gender),
           position="dodge",
           show.legend = FALSE)+
  facet_grid(~Location+Citizenship)+
  labs(y="Happiness Score",title="Happpiness related to Location-Citizenship-Gender")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_discrete(limit = c("F","M"),
                   labels=c("Female","Male"))+
  scale_y_continuous(breaks=seq(0,6,by=0.5))+
  geom_hline(yintercept=3.93,linetype=2)

```


**Plot 2: Spread of happiness scores for every category with outlier**

- Singaporean/PR have greater spread (variance)
- Off- campus foreigner students have the least spread (nearly none) but highest mean as comapared to the rest
- Outlier for a foreigner female(ID No. 5) living on-campus with the lowest happiness level=1.551724 

```{r plot2, echo=FALSE, fig.height=4}
get_box_stats <- function(y, upper_limit = max(final$happ_score) * 1.15) {
  return(data.frame(
    y = 0.95 * upper_limit,
    label = paste(
      "Mean =", round(mean(y), 2), "\n",
      "Median =", round(median(y), 2), "\n"
    )
  ))
}

outlier<-final %>% 
  filter(Location=="On campus",Citizenship=="Foreigner",id==5)

final %>%
  filter(id!=5)%>%
  group_by(Gender)%>%
  ggplot(aes(x=Gender,y=happ_score,fill=Gender))+
  geom_boxplot(show.legend=FALSE)+
  geom_jitter(shape=16, position=position_jitter(0.2), show.legend = FALSE)+
  stat_summary(fun.data = get_box_stats, geom = "text", hjust = 0.5, vjust = 0.86,size=2.5)+
  facet_grid(rows = vars(Citizenship), cols = vars(Location))+
  labs(y="Happiness Score",title="Spread of happiness scores")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_discrete(limit = c("F","M"),
                   labels=c("Female","Male"))+
  scale_y_continuous(breaks=seq(1.5,5.5,by=0.5))+
  geom_point(data=outlier,aes(x=Gender,y=happ_score),color="blue",alpha=0.8,show.legend = FALSE)+
  geom_text(data=outlier,aes(x=Gender,y=happ_score),label="(Foreigner,On Campus,Female)",nudge_y=0.3,nudge_x=0.1,size=2.5)

```

**Plot 3: Visualising Correlations**

- The smooth line shows the pattern between the score and other variables
- Females has greater confidence region so the regression region lies within it
- Males have smaller region of confidence

```{r plot3 , echo=FALSE,message=FALSE, fig.align='center', fig.height=3.5}
ggplot(final)+
  geom_line(aes(x=id,y=happ_score,
                color=Citizenship,
                linetype=Location))+
  geom_point(aes(x=id,y=happ_score,
                shape=Gender),show.legend = FALSE)+
  facet_wrap(~Gender,
             labeller =as_labeller(c(`F`="Female", `M`="Male")))+
  geom_smooth(method = 'loess',
              aes(x=id,y = happ_score))+
  theme(legend.direction = "vertical",
        plot.title = element_text(hjust=0.5))+
  labs(x="ID",y="Happiness Score", 
       title="Correlation with respect to Gender-Citizenship-Location")

```

**Plot 4: Visualising based on every variable**

```{r plot4, echo=FALSE, message=FALSE, fig.height=4}
ggpairs(final[,c(1:5)], aes(colour=Gender,alpha=0.8),
        lower=list(continuous="density", discrete="crosstable"),
        showStrips=TRUE)

```


